%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{customcv}
\usepackage[english]{babel}

\geometry{left=1.4cm, top=1.4cm, right=1.4cm, bottom=1.4cm, footskip=.5cm}

\name{Fabian}{Ockenfels}
\address{90210 Beverly Hills, California}
\mobile{(+00) 123 456 789 00}
\email{ockenfels.fabian@gmail.com}
\homepage{https://github.com/sbstnc}

\begin{document}
  \makecvheader

  \begin{multicols}{2}

  \cvsection{About me}

  As a trained mathematician I would describe myself as an analytical and rational thinker.
  I prefer sustainable, generic solutions over ad-hoc shims and advocate for flexible, intelligent software products.
  I'm a reliable, responsible and trustworthy person, capable of inspiring others.

  \cvsection{Experience}

  \begin{cventries}

    \cventry
      {Big Data Analyst}
      {Umbrella Corporation}
      {Aug. 2019 – Present}
      {
        \begin{cvitems}
          \item {Set up business intelligence tooling}.
          \item {Technical guidance.}
          \item {Vanquisher of family pizzas.}
        \end{cvitems}
      }

    \cventry
      {Big Data Engineer}
      {Initech}
      {Mar. 2017 – Aug. 2019}
      {
        \begin{cvitems}
          \item {Founding member of the big data tribe.}
          \item {Designed and implemented trending products \newline
                 algorithm on DataFlow.}
          \item {Established Airflow and Argo as workflow engines.}
          \item {Implemented and improved related products \newline
                 algorithm using Apache Spark.}
          \item {Creator and maintainer of the product history dataset.}
        \end{cvitems}
      }

    \cventry
      {Software Engineer}
      {Conglom-O}
      {Dec. 2016 – Mar. 2017}
      {
        \begin{cvitems}
          \item {Started working at Conglom-O.}
          \item {Product recommendations.}
          \item {Kafka, Java, etc.}
        \end{cvitems}
      }

  \end{cventries}

  \cvsection{Education}

  \begin{cventries}
    \cventry
      {Master of Science}
      {FH Remagen}
      {Feb. 2017 – Juli. 2016}
      {
        \begin{cvitems}
          \item {Mathematics in Finance and Life Science}
        \end{cvitems}
      }

    \cventry
      {Bachelor of Science}
      {FH Remagen}
      {Mar. 2017 – Aug. 2019}
      {
        \begin{cvitems}
          \item {Wirtschaftsmathematik}
        \end{cvitems}
      }

  \end{cventries}

  \vfill\null
  \columnbreak

  \cvsection{Skills}

  \skillgroup
    {Languages}
    {
      \skill{Scala} \skill{Kotlin} \skill{Java} \skill{C++} \skill{Python}
      \skill{Javascript} \skill{TypeScript} \skill{SQL}
    }

  \skillgroup
    {Technologies}
    {
      \skill{BigQuery} \skill{Teradata} \skill{PostgreSQL} \skill{Kafka} \skill{Spark}
      \skill{DataFlow} \skill{Airflow} \skill{Argo}
    }

  \contactinfo

  \end{multicols}

\end{document}
